### 2022-11-24 ms.rmd
Adding tree data

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp)

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable,  patchwork, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp)

```{r, tree}
# Bring in the fly tree
tree <- read.tree("./phylogeny/drosi.tre")

# Plot the tree
plot(tree, cex = 0.2)

# Ultrametric?
is.ultrametric(tree) # nope

# Grab phylo matrix
phy_vcv <- vcv(tree)
